```{r, include=FALSE}
setup_google_access_target <- "the Google Analytics properties"
```

```{r child='google-authentication-reference.Rmd'}
```

You'll need to collect the Google Analytics property IDs for the websites you want to retrieve data from.

1. Go to https://analytics.google.com/. You may have to login. These instructions are assuming you have already set up Google Analytics and have been collecting data.
2. Click on the website at the top of the navbar. It will bring you to a dropdown that shows all your websites.
3. Click on one of the websites where you'd like to retrieve data from. The URL will look something like this:

```
https://analytics.google.com/analytics/web/?authuser=1#/p<PROPERTY_ID_HERE>/reports/home
```

Copy the property ID and put it in the `ga_property_ids` part of the `_config_automation.yml` file. Repeat these same steps for all the properties you'd like to collect data for, separating the IDs by commas. Delete the example IDs we have put there as placeholders.

```
###### Google Analytics ######
refresh-ga: yes
ga_property_ids: [ 422671031, 422558989 ]
ga_googlesheet:
```

```{r, include=FALSE}
setup_refresh_field <- "`refresh-ga`"
setup_googlesheet_field <- "`ga_googlesheet`"
setup_google_sheet_destination <- "where you'd like the Google Analytics data to be saved"
```

```{r child='refresh-enabled-check.Rmd'}
```

- [ ] In `ga_property_ids`, specify the Google Analytics property IDs for the websites you'd like to collect data from. Separate property IDs with commas. Delete the example IDs we've put there.

```{r child='google-sheet-destination-option.Rmd'}
```
